Turbulence in compact to giant H~II regions

### 2023-04-28 strucfunc_paper.tex
Revisions to section 4.4

However, there are two outlier values that deserve closer attention.
NGC~595 has the lowest value of \SI{0.2}{arcsec}, which seems
unrealistically small, especially given the higher values
derived for the other sources, such as NGC~604,
that were obtained with the same instrument.
On the other hand, the 95\% credibility range extends as high as \SI{0.7}{arcsec},
which does overlap with the range for NGC~604.
If one were to take a common compromise seeing of \SI{0.7}{arcsec}
for both sources (\(s_0 = \SI{1.2}{pc}\)),
then the anticorrelation between \(m\) and \(s_0\)
%(see Figure~\ref{fig:corner-ExtraGal}a, b)
would decrease the inferred \(m\) for NGC~595 while increasing it for NGC~604,
thus making the two slopes more closely similar.

The inner Orion Nebula has the largest inferred seeing FWHM of \SI{2.4(4)}{arcsec},
which is at least two times higher than the typical seeing measured during the observations
\citep{Doi:2004a}.
However, this can be at least partially explained by the fact that the velocity map is constructed
by interpolating individual longslit observations onto a regular grid
(section~\ref{sec:longsl-echelle-spect}).
The seeing-limited resolution will only be achieved along the slits,
whereas the resolution in the perpendicular direction is determined by the slit spacing of \SI{2}{arcsec}.
Given this, the model-derived value of \(s_0\) for this source is not unreasonable.

>>>>

\startNEW
However, there are a few outlier values that deserve closer attention.
NGC~595, Hubble~V, and Hubble~X all have model-derived upper limits to the
seeing FWHM of about \SI{0.6}{arcsec}, which seems
unrealistically small, especially given the higher value
derived for NGC~604,
which was observed with the same instrument.
Unfortunately, we do not have access to the observing logs to check this,
so we suggest extra caution in interpreting the fit results for these objects. 
\stopNEW

The inner Orion Nebula has the largest inferred seeing FWHM of \NEW{\SI{1.8(2)}{arcsec}},
which is \NEW{nearly twice as high as} the typical seeing measured during the observations
\citep{Doi:2004a}.
However, this can be at least partially explained by the fact that the velocity map is constructed
by interpolating individual longslit observations onto a regular grid
(section~\ref{sec:longsl-echelle-spect}).
The seeing-limited resolution will only be achieved along the slits,
whereas the resolution in the perpendicular direction is determined by the slit spacing of \SI{2}{arcsec}.
Given this, the model-derived value of \(s_0\) for this source is not unreasonable.
